Accelerating Genetic ANN Training using the CUDA Platform

### 2010-04-18 doc/paper.tex
Tweak wording on how we gave perf numbers
git-svn-id: http://svn.scesoc.ca/evolution/trunk@79 fee98b4c-d1c3-4d34-9525-a468159e4a48
use en dash for two-author algorithm names
git-svn-id: http://svn.scesoc.ca/evolution/trunk@80 fee98b4c-d1c3-4d34-9525-a468159e4a48

Some approaches to ANN training include gradient descent, Gauss-Newton and Levenberg–Marquardt. Greedy approaches such as these seek extrema using the local behaviour of the error function and are thus susceptible to getting stuck at local extrema rather than finding the global extremum. Stochastic approaches asymptotically explore the entire search space, offering the promise of "eventually" reaching the global extremum.

@@

Item 1 is not very computationally intensive and was not parallelized. Items 2, 3 and 4 were all implemented on the CUDA platform. Performance results are given for the combined execution time of these three items.

>>>>

Some approaches to ANN training include gradient descent, Gauss--Newton and Levenberg-–Marquardt. Greedy approaches such as these seek extrema using the local behaviour of the error function and are thus susceptible to getting stuck at local extrema rather than finding the global extremum. Stochastic approaches asymptotically explore the entire search space, offering the promise of "eventually" reaching the global extremum.

@@

Item 1 is not very computationally intensive and was not parallelized. Items 2, 3 and 4 were all implemented on the CUDA platform. Performance results are given as the combined time for one generation of these last three items but exclude one-time initialization.
